\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    pdfauthor={Miraj Chamara Samarakkody},
    pdftitle={Curriculum Vitae - Miraj Chamara Samarakkody},
    pdfsubject={Curriculum Vitae},
    pdfkeywords={mathematics, differential geometry, minimal surfaces, elastic curves, Lean 4}
}

\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}
\titlespacing*{\subsection}{0pt}{8pt}{4pt}

\setlist[itemize]{leftmargin=*,topsep=2pt,itemsep=2pt,parsep=0pt}

\pagestyle{plain}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
	{\LARGE \textbf{Miraj Chamara Samarakkody}}\\[6pt]
	Phone: +1 (769) 601-6290\\
	Email: \href{mailto:miraj.samarakkody@gmail.com}{miraj.samarakkody@gmail.com}\\
	Website: \href{https://mirajcs.github.io/}{mirajcs.github.io}
\end{center}

\section*{Summary}

Assistant Professor of Mathematics at Tougaloo College with a Ph.D. from Texas Tech University. Research spans pure and applied differential geometry, with active work on variational problems. Principal Investigator on NIH- and NSF-funded research projects, with published work in differential geometry and open-source contributions to mathematical software.

\section*{Research Interests}

Differential geometry; minimal surfaces; generalized elastic curves; variational problems; geometric analysis; mathematical physics; applications to biology and data science; formalization of mathematics in Lean 4; Julia package development for machine learning and differential geometry.

\section*{Education}

\textbf{Ph.D. in Mathematics}, Fall 2021 -- Spring 2025\\
Texas Tech University, Lubbock, TX\\
Advisors: Dr. Hung Tran (Chair), Dr. \'Alvaro P\'ampano (Co-chair)

\vspace{6pt}
\textbf{B.Sc. (Honors) Special in Mathematics}, 2014 -- 2018\\
University of Peradeniya, Sri Lanka\\
Advisor: Dr. Shelton Perera

\section*{Professional Experience}
\textbf{Assistant Professor}, Spring 2025 -- Present\\
Department of Mathematics and Computer Science, Tougaloo College, MS

\vspace{6pt}
\textbf{Graduate Part-Time Instructor}, Fall 2024\\
Department of Mathematics and Statistics, Texas Tech University, TX

\vspace{6pt}
\textbf{Research Assistant}, Spring 2022 -- Summer 2024\\
Department of Mathematics and Statistics, Texas Tech University, TX\\
Mentors: Dr. Hung Tran and Dr. \'Alvaro P\'ampano

\vspace{6pt}
\textbf{Graduate Teaching Assistant}, Fall 2021\\
Department of Mathematics and Statistics, Texas Tech University, TX\\
\vspace{6pt}
\textbf{Lecturer}, 2019 -- Fall 2021\\
Department of Mathematics, University of Moratuwa, Sri Lanka

\section*{Short Visits}

\textbf{Research Mentor}, Virtual Math Circle, Department of Mathematics, Louisiana State University \hfill Summer 2025

\section*{Technical Skills}

\textbf{Programming Languages:} Python, Julia, C \\
\textbf{Mathematical Software:} Mathematica, MATLAB\\
\textbf{Typesetting:} LaTeX, Typst\\
\textbf{Theorem Proving:} Lean 4\\
\textbf{Design and Media:} Blender, Adobe Illustrator, Adobe Premiere Pro\\
\textbf{Productivity:} Microsoft Office

\section*{Teaching}

\subsection*{Tougaloo College}
\begin{itemize}
	\item MAT103 - College Algebra; Summer 2025, Summer 2026
	\item MAT221 - Calculus I; Fall 2025, Spring 2026
	\item MAT222 - Calculus II; Spring 2025, Spring 2026
	\item MAT316 - Differential Equations; Fall 2025
	\item MAT326 - Introduction to Probability; Fall 2025
	\item MAT414 - Modern Algebra; Spring 2025
	\item MAT426 - Advanced Calculus; Spring 2025, Fall 2025
	\item MAT429 - Complex Variables; Spring 2026
	\item MAT434 - Theory of Mathematical Statistics; Spring 2025, Spring 2026
\end{itemize}

\subsection*{Texas Tech University}
\begin{itemize}
	\item MATH 1452 - Calculus II with Applications; Fall 2024
\end{itemize}

\section*{Grants}

\begin{itemize}
	\item \textbf{Principal Investigator}, Institutional Development Award (IDeA), National Institute of General Medical Sciences, National Institutes of Health, Grant Number P20GM103476. Amount: \$29,317.\\
	      Project: Multivariate Statistical Analysis and Machine Learning Approaches for Heart Disease Prediction and Risk Factor Identification.
	\item \textbf{Recipient}, HBCU UP Implementation Project, Award Number 2510537.
	\item \textbf{Principal Investigator}, SCALE Program (Partnership with Purdue University). Amount: \$73,094.77.\\
	      Project: Microelectronic Workforce Development Project for Radiation-Hardening.
\end{itemize}

\section*{Fellowships}

\begin{itemize}
	\item \textbf{Dr. Shelby Hildebrand Graduate Math Fellowship}, Texas Tech University, 2023 -- 2024. Amount: \$10,000.
	\item \textbf{AT\&T Graduate Fellowship}, Texas Tech University, 2021 -- 2025. Amount: \$16,000.
\end{itemize}

\section*{Awards and Honors}

\begin{itemize}
	\item \textbf{Create Possible Scholarship}, Texas Tech University, 2022.
	\item \textbf{University Prize for Academic Excellence}, University of Peradeniya, 2018.
	\item \textbf{Peradeniya University Alumni Australia Victoria Chapter Scholarship for Academic Excellence in Mathematics}, 2015.
\end{itemize}

\section*{Publications}

\begin{itemize}
	\item M. Samarakkody. ``Formalizing the Classical Isoperimetric Inequality in the Two-Dimensional Case.'' Submitted.
	\item Y. Li, E. G\"uler, M. Toda, M. Samarakkody. ``Geometric Properties of Hypersurfaces of Right Conoids in Minkowski Spacetime.'' Submitted.
	\item A. P\'ampano, M. Samarakkody, H. Tran. ``Closed $p$-Elastic Curves in Spheres of $\mathbb{L}^{3}$.'' Journal of Mathematical Analysis and Applications, 542(2):129147, 2025.
	\item S.R.S.M.C. Samarakkody, P.G.R.S. Ranasinghe, A.A.S. Perera. ``Geometric Behavior of a Certain Class of Quotients of Finite Blaschke Products.'' International Conference on Multidisciplinary Engineering (ICMME), Post Graduate Institute of Science, University of Peradeniya, Vol. 1, 2019.
\end{itemize}

\section*{Software}

\begin{itemize}
	\item \textbf{ParametricCurves.jl} - Julia package for analyzing parametric curves.\\
	      Repository: \href{https://github.com/mirajcs/ParametricCurves.jl}{github.com/mirajcs/ParametricCurves.jl}\\
	      DOI: \href{https://doi.org/10.5281/zenodo.20140761}{10.5281/zenodo.20140761}
	\item \textbf{SymKit.jl} - Julia package for symbolic computation, supporting algebraic manipulation, differentiation, simplification, evaluation, and limits with Unicode pretty-printing.\\
	      Repository: \href{https://github.com/mirajcs/SymKit.jl}{github.com/mirajcs/SymKit.jl}\\
	      DOI: \href{https://doi.org/10.5281/zenodo.20237362}{10.5281/zenodo.20237362}
\end{itemize}

\section*{Presentations}

\subsection*{Conference Talks}
\begin{itemize}
	\item ``Closed $p$-Elastic Curves in 2-Space Forms.'' AMS Sectional Meeting (Meeting No. 1198), University of Texas at San Antonio, September 14--15, 2024.
	\item ``Closed $p$-Elastic Curves in Spheres of Lorentz-Minkowski Space.'' Texas Analysis and Mathematical Physics Symposium, Texas A\&M University, February 10, 2024.
	\item ``Geometric Behavior of a Certain Class of Quotients of Finite Blaschke Products.'' ICMME, Post Graduate Institute of Science, University of Peradeniya, March 2019.
\end{itemize}

\subsection*{Posters}
\begin{itemize}
	\item ``Formalizing the Isoperimetric Inequality in Lean 4.'' XX Red Raider Minisymposium - Geometric Analysis and Applications, Texas Tech University, April 25, 2026.
	\item ``Closed $p$-Elastic Curves in 2-Space Forms.'' Texas Geometry and Topology Conference (68th Meeting), Texas A\&M University, College Station, November 8--10, 2024.
\end{itemize}

\subsection*{Seminars}
\begin{itemize}
	\item ``From Manifold to Machines: Formalizing Differential Geometry in Lean.'' Probability, Differential Geometry and Mathematical Physics Seminar, Texas Tech University, April 24, 2026.
	\item ``On Some Variational Problems in Curves and Surfaces.'' Probability, Differential Geometry and Mathematical Physics Seminar, Texas Tech University, January 21, 2025.
	\item ``On Some Variational Problems in Differential Geometry.'' Probability, Differential Geometry and Mathematical Physics Seminar, Texas Tech University, November 1, 2023.
	\item ``Minimal Surfaces.'' Probability, Differential Geometry and Mathematical Physics Seminar, Texas Tech University, November 2, 2022.
\end{itemize}

\section*{Leadership and Community Involvement}

\begin{itemize}
	\item Member, Commission on Animal Care - Institutional Review Board (IRB), Tougaloo College, 2025 -- 2026.
	\item Judge, Kincheloe Research Symposium, Tougaloo College.
	\item Counselor, Summer Chess Camp 2024, Texas Tech University.
	\item Judge, Arts and Humanities Conference 2023, Texas Tech University.
	\item Mentor, Math Circle 2023 -- 2024, Department of Mathematics and Statistics, Texas Tech University.
\end{itemize}

\section*{Professional Memberships}

\begin{itemize}
	\item Member, American Mathematical Society, 2021 -- 2025.
	\item Member, SIAM Texas Tech University Chapter, 2021 -- 2025.
\end{itemize}

\end{document}
