
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{amssymb}

\titleformat{\section}{\normalfont\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{1.5ex}{0.5ex}

\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}

\pagestyle{empty}

\begin{document}

\begin{center}
\textbf{\large BIOGRAPHICAL SKETCH}\\[0.5em]
\textbf{Miraj Chamara Samarakkody}
\end{center}

\section*{(a) Professional Preparation}

\begin{tabular}{@{}p{2.5in}p{1.8in}p{1.5in}@{}}
University of Peradeniya, Sri Lanka & Mathematics & B.Sc. (Honors), 2018 \\
Texas Tech University, TX & Mathematics & Ph.D., 2025 \\
\end{tabular}

\section*{(b) Appointments}

\begin{tabular}{@{}p{4.5in}r@{}}
\textbf{Assistant Professor} & 2025--Present \\
\multicolumn{2}{@{}l@{}}{Department of Mathematics and Computer Science, Tougaloo College, MS} \\[0.5em]

\textbf{Research Mentor} & Summer 2025 \\
\multicolumn{2}{@{}l@{}}{Virtual Math Circle, Department of Mathematics, Louisiana State University} \\[0.5em]

\textbf{Graduate Part-Time Instructor} & Fall 2024 \\
\multicolumn{2}{@{}l@{}}{Department of Mathematics \& Statistics, Texas Tech University, TX} \\[0.5em]

\textbf{Research Assistant} & 2022--2024 \\
\multicolumn{2}{@{}l@{}}{Department of Mathematics \& Statistics, Texas Tech University, TX} \\[0.5em]

\textbf{Graduate Teaching Assistant} & Fall 2021 \\
\multicolumn{2}{@{}l@{}}{Department of Mathematics \& Statistics, Texas Tech University, TX} \\[0.5em]

\textbf{Lecturer} & 2019--2021 \\
\multicolumn{2}{@{}l@{}}{Department of Mathematics, University of Moratuwa, Sri Lanka} \\
\end{tabular}

\section*{(c) Products}

\subsection*{(i) Products Most Closely Related to the Proposed Project}

\begin{enumerate}[label=\arabic*.]
\item A. P\'ampano, \textbf{M. Samarakkody}, H. Tran, ``Closed $p$-Elastic Curves in Spheres of $\mathbb{L}^{3}$,'' \textit{Journal of Mathematical Analysis and Applications}, 542(2):129147, 2025.

\item S.R.S.M.C. Samarakkody, P.G.R.S. Ranasinghe, A.A.S. Perera, ``Geometric Behavior of a Certain Class of Quotients of Finite Blaschke Products,'' \textit{Proceedings of the International Conference on Mathematics and Mathematics Education (ICMME)}, Post Graduate Institute of Science, University of Peradeniya, Vol. 1, 2019.
\end{enumerate}

\subsection*{(ii) Other Significant Products}

\textit{Not applicable.}

\section*{(d) Synergistic Activities}

\begin{enumerate}[label=\arabic*.]

\item \textbf{Research Mentorship:} Serving as Research Mentor for the Virtual Math Circle at Louisiana State University (Summer 2025), guiding students in mathematical research and problem-solving.

\item \textbf{Grant Leadership:} Principal Investigator on the SCALE Program (Partnership with Purdue University), ``Microelectronic Workforce Development Project for Radiation-Hardening,'' funded at \$73,094.77.

\item \textbf{Institutional Service:} Member of the Commission on Animal Care -- Institutional Review Board (IRB) at Tougaloo College (2025--2026), contributing to ethical oversight of research activities.

\item \textbf{K-12 Outreach:} Mentor for Math Circle at Texas Tech University (2023--2024), developing and delivering mathematical enrichment activities for middle and high school students to foster interest in mathematics.

\item \textbf{Academic Community Engagement:} Judge for the Kincheloe Research Symposium at Tougaloo College and the Art \& Humanities Conference 2023 at Texas Tech University; Counselor for the Summer Chess Camp 2024 at Texas Tech University, promoting academic excellence and student development.

\end{enumerate}

\vfill

\end{document}
